Lens Modeling in \sw

### 2014-06-27 text/partA.tex
edits

Figure \ref{fig:6941} shows the simplest case, with two clear images
produced by a nearly-circular lens.  The centre of the lensing galaxy
is a maximum, the image nearer to the galaxy is a saddle point, and
image further away is a minimum, and these were correctly identified.
  It shows wide arcs, almost a ring.

Figure \ref{fig:6915} shows another quad.  This kind of configuration
arises when the mass is elongated and the source is displaced at an
angle to the elongation.

Figure \ref{fig:6990} shows an example of an arc that has split into
three images.  This kind of configuration, with a counter-image close
to the lensing galaxy and a more distant arc/triplet on the other
side, generically arises from an elongated mass distribution when the
source is displaced along the elongated direction.

To conclude this set of examples, Figure \ref{fig:6919} shows another
type of quad.  Actually, in this case the brightest part of the source
is only doubly imaged, but the source extends into a region that
produces four images.  We can also see from the real arrival-time
surface that a point source is a double on the verge of splitting into
a quad.  The modeler interpreted the system as a quad.  The appearance
of the arcs, looks like an arc and counter-image such as discussed
with Figure \ref{fig:6990} above.  But there is an important
difference: the long arc is closer to the galaxy, as if the arc and
counter-image have swapped roles.  This configuration arises if the
source displacement is perpendicular to the long axis of the lensing
mass.

Figure \ref{fig:6975} shows a lens with substructure in the form of a
smaller secondary galaxy.  The galaxies in such group or cluster sims
were, in fact, based on galaxies visible in the images --- but the
modelers were not told in advance whether this was the case.  The
model does not include any substructure, but otherwise is not bad.
The minimum and saddle point are correct, and the Einstein radius is
only a little underestimated.

Figure \ref{fig:6937} shows a case where substructure leads to a
poor model.

Figure \ref{fig:7022} shows another model of the same system.  In this
one, the identification of the minima and saddle points was incorrect,
and mass distribution comes out elongated East-West instead of
North-South.  The mass distribution also appears somewhat jagged and
the saddle-point contours are not as clean as in the previous
examples; these are often indicators of a problem with the model.  The
enclosed mass is, however, none the worse --- the reason is probably
that in a relatively symmetrical image configuration, the Einstein
radius is quite well constrained by the images in a fairly
model-independent way.

Figure \ref{fig:6975} shows a fairly symmetric quad.  The minima and
saddle points are correctly identified, and the orientation of the
ellipticity of the mass distribution is correctly reproduced.  The
Einstein radius is somewhat overestimated.

@@

The panel shows
a average $\kappa$ within a given radius, as a function of radius.
The red curve is the true value, and where it crosses unity (dotted
horizontal line) is the notional Einstein radius $\Theta_{\text{E, sim}}$.
  The two blue curves
are the minimal and maximal mean enclosed $\kappa$ from the internal
ensemble in \spl.  The region between the blue curves is shaded
between the radii of the innermost and the outermost images --- this
is the confidence region from the modeling.  As we see, the shaded
blue is slightly above the red curve. 
The Einstein Radius $\Theta_\text{E}$ of the model is estimated crossing the
mean enclosed $\kappa$ (not plotted) with unity.

>>>>

Let us now consider these cases in turn.

\begin{itemize}

\item Figure \ref{fig:6941} shows the simplest case, with two clear
  images produced by a nearly-circular lens.  The centre of the
  lensing galaxy is a maximum, the image nearer to the galaxy is a
  saddle point, and image further away is a minimum, and these were
  correctly identified.

\item Figure \ref{fig:6990} shows an example of an arc that has split
  into three images.  This kind of configuration, with a counter-image
  close to the lensing galaxy and a more distant arc/triplet on the
  other side, generically arises from an elongated mass distribution
  when the source is displaced along the elongated direction.

\item Figure \ref{fig:6919} shows another example of an arc plus
  counter-image, but (in contrast to Figure \ref{fig:6990}) the arc is
  closer to the lens than the counter-image. This configuration arises
  if the source displacement is perpendicular to the long axis of the
  lensing mass.  Comparing the two panels in the middle row, we see
  that the modeller interpreted arc as consisting of three images,
  whereas the sim shows a single saddle point associated with the arc.
  But the identification is not really erroneous --- we just need to
  take into account that the source is extended.  In fact, in the sim
  the brightest part of the source is only doubly imaged, but the
  source extends into a region that produces four images.  In the
  $t(x,y)$ of the sim, the hairpin-bending contours are typical of
  double on the verge of splitting into a quad.

\item Figure \ref{fig:6915} shows another quad.  This kind of
  configuration arises when the mass is elongated and the source is
  displaced at an angle to the elongation.  The minima and saddle
  points are correctly identified, and the orientation of the
  ellipticity of the mass distribution is correctly reproduced.

\item Figure \ref{fig:6975} shows a lens with substructure in the form
  of a smaller secondary galaxy.  The galaxies in such group or
  cluster sims were based on galaxies visible in the images, but the
  modelers were not told in advance whether this was the case.  The
  minimum and saddle point are correctly identified.  The mass
  distribution misses the substructure, but overall appears
  reasonable.

\item Figure \ref{fig:7025} shows a quad.  In this one, the
  identification of the minima and saddle points was incorrect, and
  mass distribution comes out elongated East-West instead of
  North-South.  The mass distribution also appears somewhat jagged and
  the saddle-point contours are not as clean as in the previous
  examples; these are often indicators of a problem with the model.
  The enclosed mass is, however, none the worse --- the reason is
  probably that in a relatively symmetrical image configuration, the
  Einstein radius is quite well constrained by the images in a fairly
  model-independent way.

\item Figure \ref{fig:7022} shows another model of the same system.

\end{itemize}

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.8\linewidth]
             {fig/007025_kappa_encl}}
  \subfigure{\includegraphics[width=0.8\linewidth]
             {fig/007022_kappa_encl}}
  \subfigure{\includegraphics[width=0.8\linewidth]
             {fig/007021_kappa_encl}} \\
  \caption{Enclosed mass \kenc from three models of the same system.
    The upper panel corresponds to the model shown in \figref{7025},
    with the image-parities incorrect by a quarter-turn.  The middle
    corresponds to \figref{7022}, where the image parities were
    correct.  The lower panel corresponds to another model, where the
    image parities were incorrect by a half-turn.}
\label{fig:kapenc_compare_faulty}
\end{figure}

@@

The panel shows a average $\kappa$ within a given radius, as a
function of radius.  The red curve is the true value, and where it
crosses unity (dotted horizontal line) is the notional Einstein radius
$\Theta_{\text{E, sim}}$.  The two blue curves are the minimal and
maximal mean enclosed $\kappa$ from the internal ensemble in \spl.
The region between the blue curves is shaded between the radii of the
innermost and the outermost images --- this is the confidence region
from the modeling.  As we see, the shaded blue is slightly above the
red curve.  The Einstein Radius $\Theta_\text{E}$ of the model is
estimated crossing the mean enclosed $\kappa$ (not plotted) with
unity. \citep[see, e.g.,][]{2002LNP...608....1C}.
